Validity of a model for a cantilever two-dimensional beam

### 2024-04-07 files/Chapter4/SP06.tex
Chapter 4 + 5 review
symbols
Overview, Chapter 3
table of symbols
chapter 4
review exam report

The authors decided on a free-free beam configuration. The natural frequencies of the Timoshenko beam theory was obtained by using frequency equations from an article by Levison and Cooke \cite{LC81}. In theoretical approach of the three-dimensional beam, two methods were considered. A commercial finite elements method (ANSYS), and a resonant ultrasound spectroscopy (RUS) technique.

@@

\subsubsection{Problem 3D-2}
Find a vector valued function $u$, satisfying the equation of motion \eqref{eq:3D_Model:EM-D} and constitutive equation \eqref{eq:3D_Model:CE-D}. Let $\Omega$ represent the reference configuration of the beam with a square cross-section.
\begin{eqnarray*}
	\Omega := \left\{ \bar{x} = \langle x,y,z \rangle \in \mathbb{R} \ | \ 0 \leq x \leq 1, \ -\frac{h}{2} \leq y, z \leq \frac{h}{2}  \right\}
\end{eqnarray*}

with $h$ the height and width of the beam. $\partial \Omega$ denotes the boundary of $\Omega$. \\

@@

@@

\subsection{Results from SP06}
The following table contains relevant results are obtained by \cite{SP06}. 
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
	\makebox[\textwidth]{
	\caption{Results from \cite{SP06} (excluding RUS).}
	\begin{tabular}{||c|c|cc|cc|c||}
		\hline
		{n} & {Measured} & {3D FEM} & {\% Error} & {Timoshenko Beam} & {\% Error} & Side \\
		\hline
		1     & 27359.6 & 27417.6 & 0,21\% & 27407.1 & 0,17\% & Flexible \\
		  	  & 27423.8 & 27515.6 & 0,33\% & 27505.3 & 0,30\% & Stiff \\
		2     & 60862   & 60882.0 & 0,03\% & 60851.1 & -0,02\% & Flexible \\
		 	  & 61098.3 & 61022.0 & -0,12\% & 60992.1 & -0,17\% & Stiff \\
		3     & 97609.5 & 97734.4 & 0,13\% & 97796.0 & 0,19\% & Flexible \\
			  & 97852.4 & 97881.5 & 0,03\% & 97945.4 & 0,09\% & Stiff \\
		4     & 161494 & 131658 & 0,12\% & 132277 & 0,60\% & Flexible \\
			  & 131732 & 131675 & -0,04\% & 132308 & 0,44\% & Stiff \\
		5     & 161352 & 161390 & 0,02\% & 163547 & 1,36\% & Stiff \\
			  & 161538 & 161517 & -0,01\% & 163611 & 1,31\% & Flexible \\
		6     & 165183 & 164887 & -0,18\% & 169108 & 2,38\% & Stiff \\
			  & 165598 & 165398 & -0,12\% & 169634 & 2,44\% & Flexible \\
		7     & 194863 & 194933 & 0,04\% & 202352 & 3,84\% & Flexible \\
		   	  & 194973 & 195032 & 0,03\% & 202115 & 3,66\% & Stiff \\
		8     & 195869 & 195977 & 0,06\% & 203319 & 3,80\% & Stiff \\
			  & 195908 & 196097 & 0,10\% & 203518 & 3,88\% & Flexible \\
		9     & 213501 &       &       & 241202 & 12,97\% & Flexible \\
			  & 213635 &       &       & 241067 & 12,84\% & Stiff \\
  {10 and 11} & 220556 &       &       & 247954 & 12,42\% & Flexible \\
			  & 220702 &       &       & 281542 & 27,57\% & Flexible \\
			  & 221010 &       &       & 247782 & 12,11\% & Stiff \\
			  & 221092 &       &       & 281408 & 27,28\% & Stiff \\
		\hline
	\end{tabular}%
	\label{tab:addlabel}%
}
\end{table}%

@@

\textcolor{red}{Onseker oor die***************}\\
In [LC81], a single frequency equation for the free-free beam is given. From the work in section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$. As the $\alpha$ for this beam is very small, the eigenvalues 9 and above will not be considered in this dissertation.\\
\textcolor{red}{Onseker oor die***************}
\end{document}

>>>>

The authors decided on a free-free beam configuration. The natural frequencies of the Timoshenko beam theory was obtained by using frequency equations from an article by Levison and Cooke \cite{LC81}. In the theoretical approach of the three-dimensional beam, two methods were considered. A commercial finite elements method (ANSYS), and a resonant ultrasound spectroscopy (RUS) technique.

@@

\subsubsection{Problem 3D-2}
Find a vector valued function $u$, satisfying the equation of motion \eqref{eq:3D_Model:EM-D} and constitutive equation \eqref{eq:3D_Model:CE-D}. Let $\Omega$ represent the reference configuration of the beam with a square cross-section.
\begin{eqnarray*}
	\Omega := \left\{ \bar{x} = \langle x,y,z \rangle \in R \ | \ 0 \leq x \leq 1, \ -\frac{h}{2} \leq y, z \leq \frac{h}{2}  \right\}
\end{eqnarray*}

with $h$ the height and width of the beam. $\partial \Omega$ denotes the boundary of $\Omega$. \label{sym:height} \\

@@

\subfile{./SuspendedBeamModel.tex}

@@

\subsection{Results from SP06}
The following table contains relevant results obtained by \cite{SP06}. 
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
	\makebox[\textwidth]{
	\caption{Results from \cite{SP06} (excluding RUS).}
	\begin{tabular}{||c|c|cc|cc|c||}
		\hline
		{n} & {Measured} & {3D FEM} & {\% Error} & {Timoshenko Beam} & {\% Error} & Side \\
		\hline
		1     & 27359.6 & 27417.6 & 0,21\% & 27407.1 & 0,17\% & Flexible \\
		  	  & 27423.8 & 27515.6 & 0,33\% & 27505.3 & 0,30\% & Stiff \\
		2     & 60862   & 60882.0 & 0,03\% & 60851.1 & -0,02\% & Flexible \\
		 	  & 61098.3 & 61022.0 & -0,12\% & 60992.1 & -0,17\% & Stiff \\
		3     & 97609.5 & 97734.4 & 0,13\% & 97796.0 & 0,19\% & Flexible \\
			  & 97852.4 & 97881.5 & 0,03\% & 97945.4 & 0,09\% & Stiff \\
		4     & 161494 & 131658 & 0,12\% & 132277 & 0,60\% & Flexible \\
			  & 131732 & 131675 & -0,04\% & 132308 & 0,44\% & Stiff \\
		5     & 161352 & 161390 & 0,02\% & 163547 & 1,36\% & Stiff \\
			  & 161538 & 161517 & -0,01\% & 163611 & 1,31\% & Flexible \\
		6     & 165183 & 164887 & -0,18\% & 169108 & 2,38\% & Stiff \\
			  & 165598 & 165398 & -0,12\% & 169634 & 2,44\% & Flexible \\
		7     & 194863 & 194933 & 0,04\% & 202352 & 3,84\% & Flexible \\
		   	  & 194973 & 195032 & 0,03\% & 202115 & 3,66\% & Stiff \\
		8     & 195869 & 195977 & 0,06\% & 203319 & 3,80\% & Stiff \\
			  & 195908 & 196097 & 0,10\% & 203518 & 3,88\% & Flexible \\
		9     & 213501 &       &       & 241202 & 12,97\% & Flexible \\
			  & 213635 &       &       & 241067 & 12,84\% & Stiff \\
  {10 and 11} & 220556 &       &       & 247954 & 12,42\% & Flexible \\
			  & 220702 &       &       & 281542 & 27,57\% & Flexible \\
			  & 221010 &       &       & 247782 & 12,11\% & Stiff \\
			  & 221092 &       &       & 281408 & 27,28\% & Stiff \\
		\hline
	\end{tabular}%
	\label{tab:addlabel}%
}
\end{table}%

@@

\end{document}

\textcolor{red}{Onseker oor die***************}\\
In [LC81], a single frequency equation for the free-free beam is given. From the work in section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$. As the $\alpha$ for this beam is very small, the eigenvalues 9 and above will not be considered in this dissertation.\\
\textcolor{red}{Onseker oor die***************}

### 2024-04-07 files/Chapter4/SuspendedBeamModel.tex
review exam report

Let $\langle w^* \ \phi^*\rangle$ represent the solution of the model problem, and $\langle w^e \ \phi^e \rangle$ the solution to the equilibrium problem. Define $\langle w \ \phi\rangle = \langle(w^*-w^e) \ \ (\phi^*-\phi^e)\rangle$ such that it represents the deviation of the beam from the equilibrium solution. Substitution verifies that $\langle w \ \phi\rangle$ satisfies the partial differential equation and boundary conditions.\\

>>>>

Let $\langle w^*, \ \phi^*\rangle$ represent the solution of the model problem, and $\langle w^e, \ \phi^e \rangle$ the solution to the equilibrium problem. Define $\langle w, \ \phi\rangle = \langle(w^*-w^e), \ (\phi^*-\phi^e)\rangle$ such that it represents the deviation of the beam from the equilibrium solution. Substitution verifies that $\langle w, \ \phi\rangle$ satisfies the partial differential equation and boundary conditions.\\

### 2024-04-07 files/Chapter4/Validity_Timo.tex
review exam report

For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method. In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived. Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.

@@

This table shows that the eigenvalues of the Timoshenko model and the two-dimensional model compare very well. The non-beam type eigenvalues are highlighted in grey. For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$. This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam. But overall the Timoshenko beam compares very well.

>>>>

For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method. In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived. Specifically, section \ref{2dFEM_EP} derives the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.

@@

This table shows that the eigenvalues of the Timoshenko model and the two-dimensional model compare very well. The non-beam type eigenvalues are highlighted in grey. For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$. This shows that as the beam becomes longer and thinner, the Timoshenko beam is a better approximation of the two-dimensional beam. But overall the Timoshenko beam compares very well.
